Improving the Replicability of Psychological Science Through Pedagogy

### 2016-09-30 paper/paper.Rmd
sofer comments 2

In two cases, in final review of the projects (after data analysis), the instructor team decided that the student's choice of key statistical test was not in fact a strong test of the original authors' primary theoretical claim. In both of these cases [@sofer2015;@proudfoot2015], the original authors had fit a multiple regression model to the data and there was not a single obvious test that corresponded directly to the authors' hypothesis. After discussion, the instructor team converged on a statistical test that they thought better corresponded to the original authors' intended hypothesis of interest. We report results from these corrected tests here. We return to this issue in the Discussion, as we believe that test selection is a critical theoretical issue in replication research [see e.g., @monin2016 for discussion].

>>>>

In two cases, in final review of the projects (after data analysis), the instructor team decided that the student's choice of key statistical test was not in fact a strong test of the original authors' primary theoretical claim. In both of these cases, the original authors had fit regression models to the data and there was not a single obvious test that corresponded directly to the authors' hypothesis. After discussion, the instructor team converged on a statistical test that they thought better corresponded to the original authors' intended hypothesis of interest. We report results from these corrected tests here. We return to this issue in the Discussion, as we believe that test selection is a critical theoretical issue in replication research [see e.g., @monin2016 for discussion].
